---
title:  "6060 Practice: RMarkdown"
author: "Brooke Charbonneau"
output:
  pdf_document:
    number_sections: yes
    toc_depth: 3
---

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# Code goes in blocks like this

# load libraries
library(tidyverse)
library(apaTables)

#Load data 
analytic_data        <- read_csv("analytic_data.csv")
analytic_data_part2       <- read_csv("analytic_data_part2.csv")
analytic_data_male40        <- read_csv("analytic_data_male40.csv")

```

# Correlations

Below are the correlations among the variables for all participants (men and women).



```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa.cor.table(analytic_data_part2,filename="Table1.doc",table.number=1)     
```

\pagebreak

# Correlations for males over 40

Below are the correlations among the variables for males over the age of 40.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa.cor.table(analytic_data_part2,filename="Table1.doc",table.number=1)
```

\pagebreak

#Agreeableness and extraversion

Below is a scatter plot between agreeableness and extraversion for men over the age of 40.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
my.scatter <- qplot(x=agreeableness,y=extraversion,data=analytic_data_male40)
my.scatter <- my.scatter + geom_smooth(method = "lm", se = FALSE, color='black')
my.scatter <- my.scatter + labs(title="Agreeableness and Extraversion for Men Over the Age of 40",
                                x="Agreeableness",y="Extraversion")
my.scatter <- my.scatter + theme_classic()
my.scatter <- my.scatter + theme(axis.line.x = element_line(colour = 'black',size=0.5, linetype='solid'),
                                 axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

print(my.scatter)
```

In men over the age of 40, there was a positive relation between agreeableness and extraversion, *r*=.40, 95% CI[.33, .47].

